---
title: "week_5_project"
author: "sahrash fatima Lab"
date: "2024-09-27"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r}
# This will open a file dialog for you to select the CSV file
df <- read.csv(file.choose())

# View the first few rows to confirm the data is loaded
head(df)
```
#NORMAL DISTRIBUTION

```{r}
mean_updrs <- mean(df$UPDRS, na.rm = TRUE)
sd_updrs <- sd(df$UPDRS, na.rm = TRUE)
pnorm(90, mean = mean_updrs, sd = sd_updrs)

```
BINOMIAL DISTRIBUTION

```{r}
pnorm(90, mean = mean_updrs, sd = sd_updrs, lower.tail = FALSE)
qnorm(0.841, mean = mean_updrs, sd = sd_updrs)

```
#POISSON DISTRUBUTION

```{r}
lambda_tremor <- mean(df$Tremor, na.rm = TRUE)
dpois(7, lambda = lambda_tremor)
ppois(7, lambda = lambda_tremor)
ppois(7, lambda = lambda_tremor, lower.tail = FALSE)

```
#BINOMIAL DISTRIBUTION

```{r}
pbinom(10, size = 100, prob = 0.2) - dbinom(0, 100, 0.2)
pbinom(10, size = 100, prob = 0.2)

```
#ALTERNATIVE CODE: 
```{r}
# Find quantile for a cumulative probability of 0.841 for UPDRS
pnorm_value <- 0.841
qnorm(pnorm_value, mean = mean_updrs, sd = sd_updrs)
# Sort UPDRS values and manually get the 84.1% quantile
sorted_updrs <- sort(df$UPDRS, na.last = TRUE)
index_841 <- floor(0.841 * length(sorted_updrs))  # Find the 84.1% index
sorted_updrs[index_841]
# Generate cumulative distribution manually and approximate quantile
cum_distribution <- ecdf(df$UPDRS)
mean_updrs <- mean(df$UPDRS, na.rm = TRUE)  # Use a different variable name like 'mean_updrs'
sd_updrs <- sd(df$UPDRS, na.rm = TRUE)

# Get the quantile for the 84.1% cumulative probability
mean_updrs
# Calculate cumulative probabilities for UPDRS values
cumulative_probabilities <- pnorm(df$UPDRS, mean = mean_updrs, sd = sd_updrs)

# Find the index corresponding to 84.1% cumulative probability
closest_index <- which.min(abs(cumulative_probabilities - 0.841))

# The corresponding UPDRS value
df$UPDRS[closest_index]

```
For the UPDRS a normal distribution approximation of the scores indicates that below 90 is common for almost 42% of the patients and scores of 158 or higher in the 84.1% quantile represent a more severe index.
The Poisson distribution can be applied to the Tremor count as most of the patient records fewer tremor frequency than our recorded value where the probability of observing 7 or more tremors an hour in the dataset is minimal.
Thus, in binomial case low probability of the event of 10 successes in 100 trials with success probability of 0.2 is to be expected due to the relative smallness of the number of successes.


