---
title: "week.5..p"
author: "sahrash fatima Lab"
date: "2024-10-02"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

# Load the dataset from the specified path
dataset <- read.csv("D:/iupui/2rd sem/R- stats/parkinsons_disease_data.csv")

# View the first few rows of the dataset to verify it loaded correctly
head(dataset)

# Check the structure of the dataset to ensure variables are correctly loaded
str(dataset)

```

```{r}
# Install and load required packages
if (!require(ggplot2)) install.packages("ggplot2", dependencies=TRUE)
if (!require(psych)) install.packages("psych", dependencies=TRUE)
if (!require(corrplot)) install.packages("corrplot", dependencies=TRUE)

library(ggplot2)
library(psych)
library(corrplot)

```


```{r}
# Plot distribution of variables and check for skewness
plot_distribution <- function(variable_name, dataset) {
  tryCatch({
    ggplot(dataset, aes(x = !!sym(variable_name))) +
      geom_histogram(bins = 30, fill = "blue", alpha = 0.7) +
      labs(title = paste("Distribution of", variable_name), x = variable_name, y = "Count") +
      theme_minimal()
  }, error = function(e) {
    return(paste("Error in plotting", variable_name, ":", e$message))
  })
}

# Variables to plot (based on dataset)
variables <- c("BMI", "UPDRS", "MoCA", "PhysicalActivity", "SystolicBP")

# Loop through and plot distributions
for (var in variables) {
  print(plot_distribution(var, dataset))
}

# Scatter plot function with regression line
scatter_plot_with_regression <- function(predictor, outcome, dataset) {
  tryCatch({
    ggplot(dataset, aes(x = !!sym(predictor), y = !!sym(outcome))) +
      geom_point() +
      geom_smooth(method = "lm", color = "red") +
      labs(title = paste("Scatter Plot of", predictor, "vs", outcome),
           x = predictor, y = outcome) +
      theme_minimal()
  }, error = function(e) {
    return(paste("Error in plotting", predictor, "vs", outcome, ":", e$message))
  })
}

# Variables to plot against UPDRS (adjust if needed)
predictors <- c("BMI", "MoCA", "PhysicalActivity", "SystolicBP")
outcome <- "UPDRS"

# Loop through and plot
for (var in predictors) {
  print(scatter_plot_with_regression(var, outcome, dataset))
}
```
```
Correlations: Because the regression lines in all of the scatter plots are almost flat, it appears that none of the variables (BMI, SystolicBP, PhysicalActivity, MoCA, and Physical Activity) have a significant linear association with UPDRS.
Distributions: Each variable's data is approximately uniform, with no significant skewness or strong trends in any direction, according to the histograms for the distributions.
